References

### 2017-04-10 cv/CoverLetter/CitiMQA_QuantitativeAnalyst.tex
Revised the Cover letter again.

I see on Citi's website that you are recruiting a quantitative
analyst to join your cross asset quantitative analysis team. In the
description of the job, you emphasised knowledge and skills in time
series analysis, C++ programming and understanding of the financial
market, which are indeed areas that I know well and am passionate
about. So I would like to ask you for your consideration.

@@

I am also finalising two other papers. One of them is about how an
investor's preference (as characterised by {\em Generalised
  Disappointment Aversion}) of an equity varies with the tail
parameters of the stationary distribution of the equity. This
result can be applied to, for example, portfolio construction and
assessment of the overall market risk. As part of the paper, I have
also done statistical analysis on the tail parameters of equities in
the S\&P 500 index, specifically, the ``Energy'', ``Consumer Staples''
and ``Information Technology'' sectors. R and C++ programming are
indispensable part of the work.

The fourth paper of mine is about estimation of the probability of very
large losses posed by portfolios whose volatility dynamics are
described by univariate GARCH(p,q) or multivariate GARCH
processes. Because the stationary distribution of such a process is
not known exactly, the aforementioned probability as well as the
related risk measures {\em Value at Risk} and {\em Expected
  Shortfall} cannot be computed precisely. In the paper I propose 
an estimator based on importance sampling and Markov chain theory and
naturally, would be more than happy to see it applied in practical
risk management. I have implemented the estimator in C++, and in
particular, have used the OpenMP directives to achieve high
performance via parallel computing.

>>>>

I see on Citi's website that you are recruiting a quantitative
analyst to join your cross asset quantitative analysis team. In the
description of the job, you emphasise knowledge and skills in time
series analysis, C++ programming and understanding of the financial
market, which are indeed areas that I know well and am passionate
about. So I would like to ask you for your consideration.

@@

I am also finalising two other papers. One of them is about how an
investor's preference (as quantified by {\em Generalised
  Disappointment Aversion}) of an equity varies with the tail
parameters of the stationary distribution of the equity. This
result can be applied to, for example, portfolio construction and
assessment of the overall market risk. As part of the paper, I have
also done statistical analysis on the tail parameters of equities in
the S\&P 500 index, specifically the ``Energy'', ``Consumer Staples''
and ``Information Technology'' sectors. R and C++ programming are
indispensable part of the work.

The fourth paper of mine is about estimation of the probability of very
large losses posed by portfolios whose volatility dynamics are
time series modeled by univariate GARCH(p,q) or multivariate
GARCH processes. Because the stationary distribution of such a process
is not known exactly, the aforementioned probability as well as the
related risk measures {\em Value at Risk} and {\em Expected
  Shortfall} cannot be computed precisely. In the paper I propose 
an estimator based on importance sampling and Markov chain theory and
naturally, would be more than happy to see it applied in practical
risk management. I have implemented the estimator in C++, and in
particular, have used the OpenMP directives to achieve high
performance via parallel computing.
